Light inextensible strings under tension in the Schwarzschild geometry

### 2019-08-27 string_physics_teacher.tex
use \geqslant instead of \geq; much classier

\noindent where units in which~$G=c=1$ are used, has been known for
over a century~\cite{schwarzschild1916}.  Here I consider the spatial
component~$ds^2= dr^2/\left(1-2M/r\right) + r^2d\phi^2$, confined to
equatorial points~($\theta=\pi/2$); we understand~$2M\leq r$
throughout.  A circular string at constant~$r$ will, trivially, have
proper length~$2\pi r$.

Considering first the radial component we may calculate the
proper length $L\left(r_1,r_2\right)$ of a string stretching
from~$r=r_1\geq 2M$ to~$r_2\geq r_1$ at constant $\theta,\phi$:

@@

\begin{figure}[p] % created by "closest_approach2.R"
\centering
\includegraphics[width=170mm]{closest_approach_selfintersecting.pdf}
\caption{Self-intersecting strings shown for $\phi\geq 0$.  Closest
  approach to the event horizon occurs at $\phi=0$ (3 o'clock) and
  $r/2M\in\left(1,1.0761\right)$; strings are symmetrical about $\phi=0$
  but for clarity only $\phi\geq 0$ is shown}
\label{closest_approach_self_intersecting}
\end{figure}

@@

\begin{figure}[p]
\centering
\includegraphics{light_start_at_r_equals_2.pdf} % created by "angle_start_at_r_equals_2.R"
\caption{Null geodesics passing through $(4M,0)$, shown for $0\leq\phi\leq 2\pi$}
\label{light_r_equals_2}
\end{figure}

>>>>

\noindent where units in which~$G=c=1$ are used, has been known for
over a century~\cite{schwarzschild1916}.  Here I consider the spatial
component~$ds^2= dr^2/\left(1-2M/r\right) + r^2d\phi^2$, confined to
equatorial points~($\theta=\pi/2$); we understand~$r\geqslant 2M$
throughout.  A circular string at constant~$r$ will, trivially, have
proper length~$2\pi r$.

Considering first the radial component we may calculate the proper
length $L\left(r_1,r_2\right)$ of a string stretching
from~$r=r_1\geqslant 2M$ to~$r_2\geqslant r_1$ at constant
$\theta,\phi$:

@@

\begin{figure}[p] % created by "closest_approach2.R"
\centering
\includegraphics[width=170mm]{closest_approach_selfintersecting.pdf}
\caption{Self-intersecting strings shown for $\phi\geqslant 0$.  Closest
  approach to the event horizon occurs at $\phi=0$ (3 o'clock) and
  $r/2M\in\left(1,1.0761\right)$; strings are symmetrical about $\phi=0$
  but for clarity only $\phi\geqslant< 0$ is shown}
\label{closest_approach_self_intersecting}
\end{figure}

@@

\begin{figure}[p]
\centering
\includegraphics{light_start_at_r_equals_2.pdf} % created by "angle_start_at_r_equals_2.R"
\caption{Null geodesics passing through $(4M,0)$, shown for
  $0\leqslant\phi\leqslant 2\pi$}
\label{light_r_equals_2}
\end{figure}
